Data Cleaning

### 2025-12-01 Data Cleaning.Rmd
Added data processing for alkalinity and hardness
Completed data processing.

## R Markdown

@@

merged

>>>>

## Alkalinity and Hardness Data

@@

summary(merged) # Both alkalinity and hardness have zero-values (no data)

merged_clean1 <- merged[(merged$alkalinity != 0) & (merged$hardness != 0),] # remove

summary(merged_clean1) # no zero values, still a very large alkalinity value

tail(sort(merged_clean1$alkalinity)) # two significant outliers (equipment likely)

merged_clean2 <- merged[merged$alkalinity < 876, ] # remove outliers

summary(merged_clean2) # successfully removed zero values and outliers
